---
name: Brendan Filkins
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: MBA
#position: Data Analytics Leader
address: Burlington, Vermont
email: brendan.e.filkins@gmail.com
github: bfilkins
linkedin: brendan-filkins
headcolor: "414141"
aboutme: Data and strategy professional with 7 years of experience scaling analytics and generating business value from data through quantitative analysis, data storytelling and bringing business stakeholders together.
output: 
  vitae::awesomecv:
    keep_tex: False
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```
# Skills

Servant Leadership - Research Design Methods - Statistics - Data Visualization - Machine Learning  
<br /> Advanced Analytics (descriptive, diagnostic, predictive, prescriptive) - Dashboard Development - Data Architecture  
<br /> Data Governance - Web Applications - Cloud Computing Frameworks - APIs - GIT and Package Development.

# Experience
```{r consulting}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Manager: Data Science and Client Strategy", "IXIS Digital", "Burlington, Vermont", "July 2021 - Present", 
  list(
    "Lead data science team on collaborative supervised and unsupervised machine learning projects in R and Python",
    "Grow start-up data analytics consulting organization through 300\\% increase in revenue with 110\\% increase in expense",
    "Synthesize complex findings for non-technical stakeholders and executive audiences to emphasize business implications",
    "Modernize technology stack, data architecture and roadmap to enable economies of scale",
    #"Use bayesian methods for statistical modeling and hypothesis testing in R",
    #"Model multi-touch channel attribution, digital personalization and conversion propensity scores",
    #"Develop executive level KPI frameworks and dashboards for digital, sales, supply chain and marketing audiences",
    "Deploy and maintain production forecasting and classification models in AWS for API access with Docker and EC2",
    #"Support team members in professional development through goal setting and advocating for development opportunities",
    "Consulting clients include: Audi, Nutrisystem, Proflowers.com, PHD media"
    ),
  "Data Scientist", "", "", "July 2020 - July 2021", 
  list(
    "Perform digital and marketing analytics/modeling to support \\$100M annual marketing spend strategies and digital customer experience", 
    "Use time-series modeling and automated anomaly detection in R; identified error in website lead submissions that boosted leads by 25\\%",
    #"Perform classification modeling and dimensional reduction in R for customer propensity scoring that is used to optimize media re-targeting",
    "Develop and deploy production interactive R Shiny web applications with Docker and AWS EC2",
    "Use survival analysis for insight on customer churn to support customer life-time value modeling",
    "Data Engineering with SQL and Python for machine learning pipelines using AWS"
    ),
  "Senior Financial Analyst", "National Life Group", "Montpelier, Vermont", "2016-2020", 
  list(
    "Interface with key business stakeholders to leverage data to support strategic decision-making",
    "Complete cost benefit analysis across operations, marketing and strategy departments",
    "Design executive level strategic KPI frameworks and develop automated Tableau dashboards",
    "Complete S\\&P Global Market Intelligence: Certified Insurance Analyst program",
    "Perform ETL, data architecture and governance with Alteryx, SQL and Python",
    "Responsbile for financial planning and analysis to support life and annuity operations teams optimize \\$200M annual budgets",
    "Deploy optimization, clustering and forecasting models in Tableau with Rserve"
    )
  ) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Education

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "Masters in Business Administration", "Champlain College", "Burlington, Vermont", "2017-2019", 
  list(
      "Course work in business leadership, finance, accounting, marketing, statistics, change management and financial decision-making"
      ),
    "Graduate Certificate in Supply Chain Analytics", "", "", "2018", 
  list(
      "Supply chain optmization modeling including linear and mixed-integer programming",
      "Analytics for supply chain decision-making including demand forecasting with ARIMA",
      "Bayesian research methods and inferential statistics"
      ),
  "BS in Psychology", "University of Vermont", "Burlington, Vermont", "2012", 
  list(
    "Course work in organizational psychology, statistics, mathematics (calculus and linear alegbra), research methods, economics, marketing, spanish, biopsychology"
      )
  ) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```


# Tools
R, SQL, Tableau, AWS, Python, Spark, Adobe Analytics, Google Analytics, GIT, Jira/Agile, HTML, Shiny, Alteryx, Excel
