---
name: Brendan Filkins
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: MBA
#position: Data Analytics Leader
address: Burlington, Vermont
www: brendanfilkins.com
email: brendan.e.filkins@gmail.com
github: bfilkins
linkedin: brendan-filkins
headcolor: "414141"
aboutme: Strategic analytics leader with nine years of experience generating business value through reproducible quantitative analysis, data strategy, technological innovation, and business collaboration.
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```
---

# Experience
```{r consulting}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Senior Director Strategic Analytics", "IXIS Digital", "Burlington, Vermont", "Feb 2023 - Present", 
  list(
    "Responsible for growing and leading data science team focused on optimizing  customer acquisition, retention and profitability",
    "Manage client relationships including: Audi, Volkswagen Credit, Nutrisystem, Proflowers.com, PHD Media",
    "Coordinate delivery for production data solutions and automation",
    #"Grow start-up data analytics consulting organization through 300\\% increase in revenue with 110\\% increase in expense",
    #"Use bayesian methods for statistical modeling and hypothesis testing in R",
    #"Model multi-touch channel attribution, digital personalization and conversion propensity scores",
    "Develop executive level KPI frameworks and dashboards for digital, sales, supply chain, and marketing audiences",
    "Lead team responsible for production forecasting and classification models"#,
    #"Support team members in professional development through goal setting and advocating for development opportunities",
    ),
  "Manager: Data Science", "", "", "July 2021 - Feb 2023",
  list(
    "Distilled complex findings for non-technical stakeholders and executive audiences to emphasize business implications",
    "Led media mix modeling to support marketing channel strategies",
    "Modernized technology stack, data architecture and roadmap to optimize capabilities and reduce costs"),
  "Analyst: Data Science", "", "", "July 2020 - July 2021", 
  list(
    "Performed controlled experiments and completed quantitative analysis to inform marketing spend and digital user experience (UX) strategies", 
    "Performed time-series modeling and automated anomaly detection in R; identified under performing channel and intervention that resulted in a 15\\% increase in lead conversion",
    "Developed and deployed production interactive R Shiny web applications with Docker and AWS",
    "Implemented survival analysis to model customer churn and estimate important features for customer life-time value",
    "Built, monitored and maintained data pipelines with SQL and Python"
    ),
  "Financial Analyst III", "National Life Group", "Montpelier, Vermont", "2016-2020", 
  list(
    "Led financial analysis and strategic planning for life and annuity operations",
    "Interfaced with key business stakeholders to leverage data to support strategic decision-making",
    "Completed cost benefit analyses across operations, finance, actuarial, marketing and strategy departments",
    #"Design executive level strategic KPI frameworks and develop automated Tableau dashboards",
    "Completed S\\&P Global Market Intelligence: Certified Insurance Analyst program",
    "Performed ETL, data architecture and governance with Alteryx, SQL and Python"
    )
  ) %>% 
  vitae::detailed_entries(role, dates, company, loc, details)
```

# Skills

Advanced Analytics (descriptive, diagnostic, predictive and prescriptive) - Statistics - Quantitative Research Methods 
<br /> Analytics Leadership - Data Visualization - Machine Learning  - A/B Testing - Data Architecture  
<br /> Data Governance - Web Applications - Dashboard Development - APIs - GIT and Package Development


# Education

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "Masters in Business Administration","Champlain College", "Burlington, Vermont", "2016-2017", 
  list(
      "Course work in business leadership, finance, accounting, marketing, statistics, change management and financial decision-making"
      ),
  "BS in Psychology", "University of Vermont", "Burlington, Vermont", "2012", 
  list(
    "Course work in organizational psychology, statistics, mathematics (calculus and linear algebra), research methods, economics, marketing, spanish, biopsychology"
      )
  ) %>% 
  vitae::detailed_entries(degree, dates, uni, loc, details)
```


# Tools

AWS (ECS, Glue, Lambda, S3, Athena), R (tidyverse, shiny, tidymodels, etc.), SQL, Python (pandas, sklearn, etc,), Docker, Tableau, Postman (APIs), Spark, Adobe Analytics, Google Analytics, GIT, Jira, Confluence, HTML, Alteryx, Excel
